SMT-Boosted Security Types for Low-Level MPC

### 2024-10-11 esop25/frontmatter.tex
checkpoint

\newcommand{\theabstract}{
  \begin{abstract}
  Secure Multi-Party Computation (MPC) is an important
  enabling technology for data privacy in modern distributed
  applications. We devevelop a new type theory to automatically
  enforce correctness, confidentiality, and integrity properties
  of protocols written in the \emph{Prelude/Overture} language
  framework. Judgements in the type theory are predicated on
  SMT verifications in a theory of finite fields. 
\end{abstract} }

>>>>

\newcommand{\theabstract}{
  \begin{abstract}
  Secure Multi-Party Computation (MPC) is an important enabling
  technology for data privacy in modern distributed applications. We
  devevelop a new type theory to automatically enforce correctness,
  confidentiality, and integrity properties of protocols written in
  the \emph{Prelude/Overture} language framework. Judgements in the
  type theory are predicated on SMT verifications in a theory of
  finite fields, which supports precise and efficient analysis. Our
  approach is compositional, scalable, and generalizes to arbitrary
  prime fields for data and key sizes.
\end{abstract} }
